Assessing the Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study

### 2024-11-12 pilot-publication/manuscript.Rmd
Minor edits in the manuscript

##### Debojit Basak`r insert_orcid_link("90000-0002-8378-9689")`
Project Research Scientist, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Johanna Berg (JB)`r insert_orcid_link("0000-0001-7553-7337")`
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Shamita Chatterjee (SC)`r insert_orcid_link("0000-0002-9460-108X")`
Department of Surgery, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Li Fell<U+00E4>nder-Tsai (LFT)`r insert_orcid_link("0000-0003-0693-6080")`
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Geeta Ghag (GG)`r insert_orcid_link("0000-0001-5561-362X")`
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

@@

##### Catherine Juillard (CJ)`r insert_orcid_link("0000-0003-0847-8933")`
Division of General Surgery, Department of Surgery, David Geffen School of Medicine at UCLA, Los Angeles, California, United States of America.

##### Vipul Nandu`r insert_orcid_link("0000-0002-3366-5610")`
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

##### Nobhojit Roy (NR)`r insert_orcid_link("0000-0003-2022-7416")`
Program for Global Surgery and Trauma, The George Institute of Global Health, New Delhi, India.

@@

##### Rajdeep Singh (RS)`r insert_orcid_link("0000-0001-6593-2624")`
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Kapil Dev Soni (KDS)`r insert_orcid_link("0000-0003-1214-4119")`
Critical and Intensive Care, JPN Apex Trauma Center, All India Institute of Medical Sciences, New Delhi, India.

##### Lovisa Strömmer (LS)`r insert_orcid_link("0000-0001-5424-7111")`
Division of Surgery, Department of Clinical Science, Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

Department of Surgery, Capio St Göran Hospital, Stockholm, Sweden.

>>>>

##### Debojit Basak `r insert_orcid_link("90000-0002-8378-9689")`
Project Research Scientist, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Johanna Berg (JB) `r insert_orcid_link("0000-0001-7553-7337")`
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Shamita Chatterjee (SC) `r insert_orcid_link("0000-0002-9460-108X")`
Department of Surgery, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Li Felländer-Tsai (LFT) `r insert_orcid_link("0000-0003-0693-6080")`
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Geeta Ghag (GG) `r insert_orcid_link("0000-0001-5561-362X")`
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

@@

##### Catherine Juillard (CJ) `r insert_orcid_link("0000-0003-0847-8933")`
Division of General Surgery, Department of Surgery, David Geffen School of Medicine at UCLA, Los Angeles, California, United States of America.

##### Vipul Nandu `r insert_orcid_link("0000-0002-3366-5610")`
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

##### Nobhojit Roy (NR) `r insert_orcid_link("0000-0003-2022-7416")`
Program for Global Surgery and Trauma, The George Institute of Global Health, New Delhi, India.

@@

##### Rajdeep Singh (RS) `r insert_orcid_link("0000-0001-6593-2624")`
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Kapil Dev Soni (KDS) `r insert_orcid_link("0000-0003-1214-4119")`
Critical and Intensive Care, JPN Apex Trauma Center, All India Institute of Medical Sciences, New Delhi, India.

##### Lovisa Strömmer (LS) `r insert_orcid_link("0000-0001-5424-7111")`
Division of Surgery and Oncology, Department of Clinical Science, Intervention and Technology (CLINTEC),  and Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.
